### 2019-07-31 thesis.tex
* thesis.tex: Summary: another day writing the thesis...
got tired for today

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
  brief, but comprehensive, description of the scales and characteristics of
  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter in the universe is in the plasma state\cite{may}. Under
cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
around galaxies or in the atmosphere of cold stars have a strong reaction to
electromagnetic fields, exhibiting the characteristic collective behavior of
plasmas\cite{tsypa,peratt2014}.
Since this ubiquity of plasmas in space came as a fact, astrophysicists and
plasma physicists have been increasingly exchanging knowledge, with plasma
physics providing theoretical background and laboratory models that might help
with the interpretation and physical explanation of astrophysical observations,
and astrophysics confirming theoretical predictions of plasma physics with
observations of phenomena that are unique to space plasma\cite{tsypa,Kulsrud2005}.

The absolute majority of the plasma observed in space is far away from us,
being accessible only through analysis of the electromagnetic spectrum
emitted from their quite remote location. A fortunate exception to this
fact is the plasma in our solar system.

% The accessibility to
% direct, in situ measurements, highly resolved remote sensing and high-resolution
% spectroscopy make of the solar plasma the right choice for our analysis.

>>>>

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
  brief, but comprehensive, description of the scales and characteristics of
  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter in the universe is in the plasma state\cite{may}. Under
cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
around galaxies or in the atmosphere of cold stars have a strong reaction to
electromagnetic fields, exhibiting the characteristic collective behavior of
plasmas\cite{tsypa,peratt2014}.
Since this ubiquity of plasmas in space came as a fact, astrophysicists and
plasma physicists have been increasingly exchanging knowledge, with plasma
physics providing theoretical background, computational and laboratory models
that might help with the interpretation and physical explanation of astrophysical
observations, and astrophysics confirming theoretical and computational
predictions on plasma physics with observations of phenomena that are unique
to space plasma\cite{tsypa,Kulsrud2005}.

On that regard, the results obtained during this graduate research can be
found on both sides of this mutual contribution. In \cite{Tigik2016a},
\cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
numerical evidence of plasma processes that might aid in the interpretation
and accurate modeling  of phenomena observed in the solar plasma. While in
\cite{Tigik2017a}, we introduce a new equation depicting an unknown process
and numerically analyze it in the context of solar physics; its existence
outside theory, however, will depend on the development of more advanced
space probes to be confirmed. The choice for applying our theory to
phenomena observed in the solar plasma, and not in some remote space plasma,
now became evident. The accessibility to direct, in situ measurements,
highly resolved remote sensing and high-resolution spectroscopy made the
solar plasma the right choice for our analysis.

% The absolute majority of the plasma observed in space is far away from us,
% being accessible only through analysis of the electromagnetic spectrum
% emitted from their quite remote location. A fortunate exception to this
% fact is the plasma in our solar system.
